---
title: "Data Wrangling Project 1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}

# library("checkpoint", lib.loc="~/R/win-library/3.3")
# checkpoint("2017-01-01")
library("tidyr", lib.loc="~/R/win-library/3.3")
library("dplyr", lib.loc="~/R/win-library/3.3")
library("readr", lib.loc="~/R/win-library/3.3")


# Load data into RStudio

refine_original <- read_csv("~/Springboard/Data Wrangling/refine_original.csv")

## Create refine_clean document to make changes to.

refine_clean <- refine_original

# Clean up brand names

refine_clean$company <- tolower(refine_clean$company)

refine_clean$company[1] <- "philips"
refine_clean$company[2] <- "philips"
refine_clean$company[3] <- "philips"
refine_clean$company[4] <- "philips"
refine_clean$company[5] <- "philips"
refine_clean$company[6] <- "philips"
refine_clean$company[10] <- "akzo"
refine_clean$company[11] <- "akzo"
refine_clean$company[14] <- "philips"
refine_clean$company[15] <- "philips"
refine_clean$company[16] <- "philips"
refine_clean$company[22] <- "unilever"

# Separate product code and number

refine_clean <- refine_clean %>%
  separate('Product code / number', c("product_code", "product_number"), sep = "-")

# Add product categories

factor_product_code <- factor(refine_clean$product_code)

factor_product_categories <- factor(refine_clean$product_code)
levels(factor_product_code) <- c("Smartphone", "Tablet", "TV", "Laptop")

refine_clean %>%
  select (product_code) %>%
  mutate(categories = factor_product_code)
  
refine_clean <- refine_clean %>% 
  mutate(categories = factor_product_code)

# Add full address for geocoding

refine_clean %>%
  select(address, city, country) %>%
  mutate(full_address = paste(address, city, country, sep = ','))
  
refine_clean <- refine_clean %>% mutate(full_address = paste(address, city, country, sep = ','))

# Add 4 binary columns for product (product_smartphone, product_tv, product_laptop and product_tablet) 
# and 4 binary columns for company (company_philips, company_akzo, company_van_houten and 
# company_unilever)

refine_clean %>%
  select(company) %>% 
  mutate(company_akzo = ifelse(company == "akzo", 1,0), 
         company_philips = ifelse(company == "philips", 1,0),    
         company_unilever = ifelse(company == "unilever", 1,0), 
         company_van_houten = ifelse(company == "van houten", 1,0)) 
  
refine_clean <- refine_clean %>% 
  mutate(company_akzo = ifelse(company == "akzo", 1,0), 
         company_philips = ifelse(company == "philips", 1,0),    
         company_unilever = ifelse(company == "unilever", 1,0), 
         company_van_houten = ifelse(company == "van houten", 1,0))

refine_clean %>%
  select(categories) %>%
  mutate(product_smartphone = ifelse(categories == "Smartphone",1,0), 
         product_tablet = ifelse(categories == "Tablet",1,0), 
         product_tv = ifelse(categories == "TV",1,0), 
         product_laptop = ifelse(categories == "Laptop",1,0))
  
refine_clean <- refine_clean %>% 
  mutate(product_smartphone = ifelse(categories == "Smartphone",1,0), 
         product_tablet = ifelse(categories == "Tablet",1,0), 
         product_tv = ifelse(categories == "TV",1,0), 
         product_laptop = ifelse(categories == "Laptop",1,0))

refine_clean

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
